Insert the article title here

### 2018-05-16 writeup/manuscript.tex
Some details added to manuscript
Details about screen resolution, distance, and stim size

The display was presented on a 17-inch CRT monitor with a resolution of $1024 \times 
768$. Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

@@

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
\caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
\end{figure}

>>>>

The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 
1050$. However, due to a miscommunication, some participants (\textbf{get exact numbers from script}) were run at $1024 \times 768$ or $1600 \times 1200$. Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. Each line segment had a length of $\approx$$1.6^{\circ}$ of visual angle irrespective of screen resolution. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

@@

% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
\begin{table*}
	\centering
	\small
	\begin{tabular}{cc|c}
	    Experiment	    &	Resolution	     & Size of stim \\
		\hline
		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
	\end{tabular}
	\caption{Size of stimuli for each experiment and screen resolution}
	\label{tab:Screen_Res}
\end{table*}

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed. Participants, were sat $\approx$47cm from the screen. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
\caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
\label{fig:between_para_rt}
\end{figure}
